Dependent Object Types

### 2012-07-01 doc/semester/report.tex
clarif

\subsubsection{Polymorphic Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type. We
can choose to make the lists invariant or covariant in the element
type by fixing the lower bound of the declaration to the upper bound
or to $\Bot$, respectively.

>>>>

\subsubsection{Polymorphic Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type. We
can choose to make the lists invariant or covariant in the element
type by fixing the lower bound of the $\mi{Elem}$ re-declaration to
the upper bound or to $\Bot$, respectively.
